### 2017-06-04 src/mstats3.tex
Added ms03 hypothesis testing.

    \section{Hypothesis Testing}
        \subsection{Power of a test}
            The power of a test is the probability of rejecting the null hypothesis, when the null hypothesis is false.The power of a test is the probability of rejecting the null hypothesis, when the null hypothesis is false.

        \subsection{Test for diffrence between means of two normal distributions}
            (Including approximation)
        \subsection{Test for population proportion and for mean of a poisson distribution}
        \subsection{Test for diffrence between population proportions and means of a poisson distribution}
        \subsection{Test $H_0: \rho = 0$ for a bivariate normal population}

>>>>

    \section{Hypothesis Testing}
        \subsection{Power of a test}
            The power of a test is the probability of rejecting the null hypothesis, when the null hypothesis is false. The power of a test is the probability of rejecting the null hypothesis, when the null hypothesis is false. This can be expressed as:
            \\
            $$1 - P(\text{Type II Error})$$
            \\
            To find the probability of a Type II error, consider the following hypothesis:
            \begin{align*}
            H_0&: \mu = 50   \\
            H_1&: \mu \leq 50
            \end{align*}
            To find the probability of a type II error, we need to find the values of the test statistic were we reject $H_0$.\\
            \begin{align*}
                -1.34 &= \dfrac{\bar{X}-50}{\dfrac{21}{\sqrt{36}}} \\
                        &= 45.31
            \end{align*}
            So we reject $H_0$ when $\bar{X} \leq 45.31$. If $\mu = 43$ what is $P(\text{Type II error})$. So we need to find $P(\text{Accepting } H_0 | H_0 \text{ is false})$, thus:
            \begin{align*}
            P(\bar{X} > 45.31 | \mu = 43) &= 1 - \phi\left(\dfrac{45.31 - 43}{\dfrac{21}{\sqrt{36}}}\right) \\
                                          &= 0.255
            \end{align*}
            So the power of the test would be $1 - 0.255 = 0.745$.

            %  of accepting $H_0$ given the $\mu = 26$. If the signifcance level of the test is $0.09$ then the critical value would be $-1.34$, and we will let the $\sigma=21$ and $n=36$.

            % Now we need to find the value of the test statistic in which we reject the null hypothesis:
            % Si

        \subsection{Test for diffrence between means of two normal distributions}
            (See SS05 Test for diffrence in means) (Including normal approximations)

        \subsection{Test for population proportion}
            (See SS04 Test for proportion)

        \subsection{Test for mean of a poisson distribution}
            (See SS04 Poisson hypothesis test)

        \subsection{Test for diffrence between population proportions and means of two poisson distribution}
            We use a normal approximation to test the difference between population proportions and means of a two poisson distribution, pooling their variances when $H_0$ is true.
            \\\\
            For example if $p_1 = \dfrac{205}{250}$ and $p_2 = \dfrac{137}{250}$ and $H_0: p_1 = p_2$, then $\hat{p} = \dfrac{205+137}{250+250} = \dfrac{342}{500} = \dfrac{171}{250}$
            \\\\
            (Couldnt find any questions on this)

        \subsection{Test $H_0: \rho = 0$ for a bivariate normal population}
            (See SS03 Testing the correlation coefficent)

### 2017-06-04 src/stats3.tex
Added table of contents.
Removed new pages and created files for MS03 and MS04.
Added ms03 hypothesis testing.

\chapter*{Statistics 3}

@@

    \newpage
    \subsection{Contingency Tables}
        So far we have looked at the frequency a single event happens, but sometimes your interested in the frequencies of two criteria happening.

@@

    \newpage
    \subsection{Yates Correction}
        For contingency tables that are 2x2 we must use yate's correction since it produces a more accurate result.

@@

\newpage
\section{Distribution free methods}
    Distribution free test's are tests that do not require the data to follow a particular distribution. Their are four Distribution free methods you need to know:

@@

    \newpage
    \subsection{The Sign Test}

@@

    \newpage
    \subsection{Wilcoxon Signed-rank Test}

@@

    \newpage
    \subsection{Mann-Whitney U-Test}

@@

    \newpage
    \subsection{Kruskal-Wallis Test}
        Kruskal-Wallis test is a non-parametric version of an ANOVA test. The test determins if their is a difference between some samples. We use this test instead of an ANOVA test if the data is not normally distributed.

@@

        \begin{step}{Conclusion}
        $9.74 > 5.991$ so reject $H_0$, samples are not from identical populations
        \end{step}
        \end{example}

\newpage
\section{Correlation}
    \newpage
    \subsection{Spearman's Rank Correlation Coefficent}

@@

    \newpage
    \subsection{Testing the correction coefficient}
        We may be interested in conducting a test to show their is no correlation between two random variables. First we find the correlation coefficient, then get the critical value from the appropriate table.

>>>>

\cchapter{Statistics 3}

@@

    \subsection{Contingency Tables}
        So far we have looked at the frequency a single event happens, but sometimes your interested in the frequencies of two criteria happening.

@@

    \subsection{Yates Correction}
        For contingency tables that are 2x2 we must use yate's correction since it produces a more accurate result.

@@

        \end{example}
\section{Distribution free methods}
    Distribution free test's are tests that do not require the data to follow a particular distribution. Their are four Distribution free methods you need to know:

@@

    \subsection{The Sign Test}

@@

    \subsection{Wilcoxon Signed-rank Test}

@@

    \subsection{Mann-Whitney U-Test}

@@

    \subsection{Kruskal-Wallis Test}
        Kruskal-Wallis test is a non-parametric version of an ANOVA test. The test determins if their is a difference between some samples. We use this test instead of an ANOVA test if the data is not normally distributed.

@@

        \begin{step}{Conclusion}
        $9.74 > 5.991$ so reject $H_0$, samples are not from identical populations
        \end{step}
        \end{example}
\section{Correlation}
    \subsection{Spearman's Rank Correlation Coefficent}

@@

    \subsection{Testing the correlation coefficient}
        We may be interested in conducting a test to show their is no correlation between two random variables. First we find the correlation coefficient, then get the critical value from the appropriate table.
